GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator

### 2022-08-25 src/tex/ms.tex
[showyourwork] overleaf sync

% Define document class
\documentclass[twocolumn]{aastex631}
\usepackage{showyourwork}

@@

% Title
\title{An open source scientific article}

% Author list
\author{@palumbom}

% Abstract with filler text
\begin{abstract}
    Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
    Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
    Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
    Donec vehicula augue eu neque, morbi tristique senectus et netus et.
    Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
    Phasellus eu tellus sit amet tortor gravida placerat.
    Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
    Praesent eget sem vel leo ultrices bibendum.
    Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
    Curabitur auctor semper nulla donec varius orci eget risus.
    Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
    Duis eget orci sit amet orci dignissim rutrum.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{sec:intro}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit.
Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae, felis.
Curabitur dictum gravida mauris, consectetuer id, vulputate a, magna.
Donec vehicula augue eu neque, morbi tristique senectus et netus et.
Mauris ut leo, cras viverra metus rhoncus sem, nulla et lectus vestibulum.
Phasellus eu tellus sit amet tortor gravida placerat.
Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
Praesent eget sem vel leo ultrices bibendum.
Aenean faucibus, morbi dolor nulla, malesuada eu, pulvinar at, mollis ac.
Curabitur auctor semper nulla donec varius orci eget risus.
Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollici- tudin vel, wisi.
Morbi auctor lorem non justo, nam lacus libero, pretium at, lobortis vitae.
Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna.
Morbi ac orci et nisl hendrerit mollis, suspendisse ut massa, cras nec ante.
Pellentesque a nulla cum sociis natoque penatibus et magnis dis parturient.
Aliquam tincidunt urna, nulla ullamcorper vestibulum turpis.
Pellentesque cursus luctus mauris \citep{Luger2021}.

\bibliography{bib}

>>>>

% Define document class
\documentclass[twocolumn]{aastex63}
\usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{xcolor}

% for showing code in appendix
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% citation aliases
\defcitealias{Lohner-Bottcher2019}{L19}
\defcitealias{Lohner-Bottcher2018}{L18}

% new commands
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\ms}{{\rm m\ s}^{-1}}
\newcommand{\cms}{\ {\rm cm\ s}^{-1}}
\newcommand{\kms}{\ {\rm km\ s}^{-1}}
\newcommand{\Halpha}{H$\alpha$}
\newcommand{\grass}{\texttt{GRASS}}
\newcommand{\PSUAA}{Department of Astronomy \& Astrophysics, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA}
\newcommand{\PSUCEHW}{Center for Exoplanets and Habitable Worlds, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA}
\newcommand{\PSETI}{Penn State Extraterrestrial Intelligence Center, 525 Davey Laboratory, The Pennsylvania State University, University Park, PA, 16802, USA}
\newcommand{\PSUStats}{Center for Astrostatistics, The Pennsylvania State University, University Park, PA, 16802, USA}
\newcommand{\PSUCDS}{Institute for Computational and Data Sciences, The Pennsylvania State University, 525 Davey Laboratory, University Park, PA 16802, USA}

% eric comments
\definecolor{ebf}{rgb}{0.4, 0.0, 0.6}
\newcommand{\ebf}[1]{\textcolor{ebf}{\bf [EBF: #1]}}

% questions/michael comments
\definecolor{mlp}{rgb}{0.294, 0.612, 0.827}
\newcommand{\mlp}[1]{\textcolor{mlp}{\bf [MLP: #1]}}

% revision stuff
% \definecolor{cedit}{rgb}{1.0, 0.25, 0.25}
% \newcommand{\revise}[1]{\textcolor{cedit}{\textbf{#1}}}
\newcommand{\revise}[1]{#1}

% \definecolor{cedittwo}{rgb}{1.0, 0.25, 1.0}
% \newcommand{\revisetwo}[1]{\textcolor{cedittwo}{\textbf{#1}}}
\newcommand{\revisetwo}[1]{#1}

% bibliography
\usepackage{natbib}
\bibliographystyle{aasjournal}

% header information
\shorttitle{GRASS: Granulation and Spectrum Simulator}
\shortauthors{M.L. Palumbo III et al.}

@@

% Title
\title{GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator}

% Author list
\author[0000-0002-4677-8796]{Michael L. Palumbo III}
\affiliation{\PSUAA}
\affiliation{\PSUCEHW}

\author[0000-0001-6545-639X]{Eric B. Ford}
\affiliation{\PSUAA}
\affiliation{\PSUCEHW}
\affiliation{\PSUCDS}
\affiliation{\PSUStats}
\affiliation{Institute for Advanced Study, 1 Einstein Drive, Princeton, NJ, 08540, USA}

\author[0000-0001-6160-5888]{Jason T. Wright}
\affiliation{\PSUAA}
\affiliation{\PSUCEHW}
\affiliation{\PSETI}

\author[0000-0001-9596-7983]{Suvrath Mahadevan}
\affiliation{\PSUAA}
\affiliation{\PSUCEHW}

\author[0000-0002-5013-5769]{Alexander W. Wise}
\affiliation{\PSUAA}
\affiliation{\PSUCEHW}

\author{Johannes L{\"o}hner-B{\"o}ttcher}
\affiliation{High-Altitude Observatory, National Center for Atmospheric Research, 3080 Center Green Drive, Boulder, CO 80301, USA}

\correspondingauthor{Michael L. Palumbo III}
\email{palumbo@psu.edu}

%% === abstract === 
\begin{abstract}
Owing to recent advances in radial-velocity instrumentation and observation techniques, the detection of Earth-mass planets around Sun-like stars may soon be primarily limited by intrinsic stellar variability. Several processes contribute to this variability, including starspots, pulsations, and granulation. Although many previous studies have focused on techniques to mitigate signals from pulsations and other types of magnetic activity, granulation noise has to date only been partially addressed by empirically-motivated observation strategies and magnetohydrodynamic simulations. To address this deficit, we present the GRanulation And Spectrum Simulator (\grass), a new tool designed to create time-series synthetic spectra \revise{with granulation-driven variability} from spatially- and temporally-resolved observations of solar \revise{absorption lines.} In this work, we present \grass, detail its methodology, and validate its model against disk-integrated solar observations. As a first-of-its-kind empirical model for spectral variability due to granulation in a star with perfectly known center-of-mass radial-velocity behavior, \grass\ is an important tool for testing new methods of disentangling granular line-shape changes from true Doppler shifts. 
\end{abstract}

\keywords{Astronomy software, Exoplanet detection methods, High resolution spectroscopy, Solar granulation, Stellar granulation}

% Main body with filler text
%% === introduction === 
\section{Introduction} \label{intro}
Since the detection of the first exoplanet orbiting a main sequence star \citep{Mayor1995}, the radial velocity (RV) method has enabled the discovery of several hundred planets to date \citep[see the NASA Exoplanet Archive;][]{Akeson2017}. Despite these successes, the RV method will \revise{need additional development to address stellar variability} and characterize Earth-analog planets around solar-type stars. In principle, the RV method uses the planet-induced Doppler reflex motion of host stars to infer the existence of planetary companions. In practice, the host stars exhibit intrinsic astrophysical variability that complicate or preclude the measurement of minute reflex velocities due to smaller, Earth-mass planets. Although advances in instrumentation have dramatically improved spectrograph stability and spectral sensitivity, the challenges posed by intrinsic stellar variability remain a significant barrier to the discovery of lower-mass, rocky planets \revise{in or near the habitable zone of other stellar systems.} \par

Several physical mechanisms, which operate on many \revise{different} timescales, drive stellar variability, including pulsations, magnetic activity, and granulation \revise{(for a detailed review of these and other phenomena see \citealt{Meunier2021})}. Pulsations refer to the rich spectrum of acoustic modes excited by instabilities in near-surface convection. For dwarf F-, G-, and K-type (FGK) stars, the principal pulsations occur on timescales of minutes and lead to residual Doppler velocity amplitudes large enough to be problematic for the search for Earth-like exoplanets (i.e., \revise{multiple} tens of centimeters per second \revise{from pulsations alone, compared to the $\sim$10$\cms$ signal expected for an Earth-twin}; e.g., \citealt{O'Toole2008} and \citealt{Michel2008}). Recently, \citet{Chaplin2019} have shown that carefully-planned exposure times equal to or greater than the period of the principal $p$-mode can effectively mitigate the observed pulsation amplitude down to the $0.1\ \ms$ level necessary for Earth-twin detection. \par

In comparison to pulsations alone, stellar magnetic activity has posed a relatively complex barrier. Starspots, cooler photospheric regions where penetrating magnetic fields inhibit surface convection, produce a rotationally-modulated, wavelength-dependent flux deficit that alters the shape of spectral lines and can therefore mimic the Doppler wobble induced by a planetary companion. In the chromosphere, concentrated magnetic field lines can produce bright regions known as plages\revise{, which tend to spatially coincide with smaller-area photospheric faculae, introducing} further perturbations. The behavior of these chromospheric regions is complicated: not only do they exhibit more complex center-to-limb brightness variations, but they can be upwards of an order-of-magnitude more extended in area than spots \citep[e.g.,][]{Chapman2001, Meunier2010}. Indeed, posited planets have been shown to actually be stellar activity \revise{masquerading as Keplerian signals} (e.g., \citealt{Robertson2014} and potentially \citealt{Jeffers2014}). In one especially insidious case, stellar activity coupled with the observing window function led to the false detection of an Earth-mass planet in the $\alpha$ Cen B system \citep{Dumusque2012, Rajpaul2016}.  \par

Approaches to mitigating spurious velocities introduced by stellar activity have been multifaceted. In the observational realm, suspected planets with orbital periods near integer multiples of the stellar rotation period are generally disregarded since spot groups can persist for multiple stellar rotations and inject power into harmonics of the rotation period \citep{Robertson2014}. Recent astrophysical insights into radial velocity ``jitter" have also produced guidance for identifying and prioritizing stars with minimal intrinsic radial velocity variability \citep{Luhn2020}. To combat activity-induced noise in observed stars, astronomers have used different spectral lines, such as \Halpha\ \citep[e.g.,][]{Kurster2003, Hatzes2015} and the Ca H\&K doublet \citep[e.g.,][]{Wilson1968, Wright2004, Isaacson2010}, to simultaneously diagnose activity in stellar photospheres and chromospheres. However, these activity indicators are not universally exploitable: diagnostic lines will show variability among stars of differing spectral types, and even different tracers may differ on the same star. Often, different indicators must be calibrated to suit specific instrumental spectral ranges, especially in the case of M dwarfs \citep{Robertson2016}. \par

Recently, astronomers have begun applying advanced statistical models to RV data series in an attempt to disentangle activity from true Doppler shifts. Gaussian Process (GP) models for stellar variability have shown particular promise in separating out these two effects \citep[e.g.,][]{Haywood2014, Rajpaul2015,Jones2017}. \revise{Indeed, a large blind test conducted in \citet{Dumusque2017} suggested that GP-based analyses provided a promising way to model correlated signals due to stellar variability and could assist with extracting short-period planetary signals with low RV semi-amplitudes in the presence of stellar variability \citep{Dumusque2016}.} To aid in the \revise{further} development of these novel statistical methods, the community has developed algorithms to simulate the photometric and spectroscopic impacts of magnetically-active regions present on the stellar photosphere \citep[e.g.,][]{Herrero2016, Boisse2012, Dumusque2014}. The respective tools produced in these publications, \texttt{StarSim} and \texttt{SOAP 2.0}, have seen widespread use, since they are able to efficiently produce simulated data sets such as those used in the development of GP models \citep[e.g.,][]{Rajpaul2015, Jones2017, Gilbertson2020}. \par

Astronomers have also used our nearest star, the Sun, as a tool to understand the RV impact of individual magnetic features. For example, \citet{Haywood2016} use simultaneous observations of sunlight reflected off the asteroid 4/Vesta and full-disk solar observations from NASA's Solar Dynamics Observatory (SDO) to show that observational proxies for stellar plage coverage may enable better inference of activity-induced RV variations. Follow-up direct observations of the Sun with a dedicated solar telescope \revise{feed into the HARPS-N spectrograph \citep{Dumusque2015, Phillips2016, CollierCameron2019}} have reinforced this finding \citep{Milbourne2019}. \par

Although astronomers have made strides toward understanding activity from observational, theoretical, and statistical standpoints, novel approaches will be required to overcome another principal obstacle to centimeter-per-second precision RVs: granulation. Granules, individual magnetoconvective cells which blanket the surfaces of cool stars, are comprised of hot and bright upwelling plasma, surrounded by rings of cooler, denser downwelling plasma known as intergranular lanes. The collective motion of granules and larger convective cells known as ``supergranules" can introduce RV perturbations on the order of meters per second on timescales ranging from minutes to days \revise{\citep{Rieutord2010, Rincon2018}}. Unlike spots and plages resulting from activity, these convective phenomenon are not rotationally modulated, and so do not exhibit the same quasi-periodic time dependence. Therefore, distinct statistical methods and observational techniques may be required to distinguish spectral variability due to granulation from true Doppler shifts. \par

Although an effective treatment for granular noise has not been devised, the physical processes by which granules perturb spectral lines is well-understood. In disk-integrated flux, typical absorption lines for solar-type stars exhibit a characteristic ``C"-shaped asymmetry that is observable in the line bisector curve \citep{Stathopoulou1993}. This characteristic shape results from the distinct motions within granules: more light is emitted by blueshifted upwelling plasma in granules compared to the redshifted downwelling plasma in lanes. An asymmetric absorption line results when the light from these distinct components is combined \citep{Gray2008}.

In disk-resolved observations, solar line bisectors vary in shape with limb position (see Figure~\ref{fig:one} and \S\ref{data}). At disk-center, typical bisectors exhibit the characteristic ``C"-shape seen in disk-integrated light. Toward the limb, however, bisectors become distorted, more resembling a ``\textbackslash"-shape. This transformation is an effect of viewing angle: at disk-center, the line of sight passes down vertically through the convective cell, whereas at the limb, the granules are viewed in profile, sampling different line-of-sight velocities. Due to these effects and their short lifetime (of order minutes), granules induce spectral perturbations that vary with time in both disk-resolved and disk-integrated light. \par

Thus far, attempts to quantify the precise RV impact of granulation-induced line perturbations have been conducted via complex magnetohydrodynamic (MHD) simulations of small patches of the stellar surface, as in \citet{Cegla2018, Cegla2019a}. Using their MHD \citep[from][]{Vogler2005} and radiative transfer \citep[from][]{Socas-Navarro2015} simulations, these authors synthesized realistic disk-resolved Fe \textsc{I} 6302 \AA\ absorption line profiles. In \citet{Cegla2019a}, the authors then tiled a sphere with simulated patches to model a star and reconstruct a disk-integrated line profile. Using this approach, they were able to show that diagnostics of line bisector shape strongly correlated with the size of the measured spurious RV shift. However, these results are based on the synthesis of a single line. Real stellar spectra contain a myriad of lines with varying formation heights, magnetic sensitivity, etc. Given the computational time required to first conduct the magnetoconvective simulations and then run the radiative transfer, this approach is not \revise{currently} feasible for generating full synthetic spectra with dense time sampling. \revise{Moreover, the amplitude of granular variability naturally depends on the assumptions and physical simplifications made in solving the MHD and radiative transfer equations. Likewise, the presence, strength, and configuration of magnetic fields can greatly impact the inferred RV RMS. For example, \citet{Sulis2020} find an RV RMS of $\sim$0.507\ $\ms$, similar to the value observed by \citet{Palle1999}. Yet with the inclusion of strong magnetic fields, \citet{Cegla2019a} find a much smaller amplitude of only $\sim$10$\cms$.} \par

\input{captions/fig1.tex}

Although these sorts of MHD simulations have yielded great physical insight, developing practical solutions to address convectively driven RV noise will require \revise{new, complementary} approaches. As we have seen from other astronomers' solar observations and data-driven photospheric models \citep[e.g.,][]{Dumusque2014, Haywood2016}, we can glean a great deal of practical knowledge from codes designed to produce observationally-informed synthetic data sets. \revise{Indeed, \citet{Sulis2017} indicate that simulated data sets could be used to train detection processes that are normally strongly affected by granular noise.} Although \revise{simulation tools such as} \texttt{StarSim} and \texttt{SOAP 2.0} have had great success modeling line perturbations from stellar active regions, neither includes a comprehensive treatment of time-variable perturbations from granulation. \revise{Other past works have used the observed and simulated properties of granules \citep{Meunier2015} and supergranules \citep{Meunier2019, Meunier2020a} to assess the impact of these convective motions on exoplanet detection prospects, though they only provide velocities and not spectra.} To fill in \revise{these gaps,} we have developed an observationally-informed simulation tool to create synthetic spectra with time-resolved, granulation-induced variability. We dub this tool \texttt{GRASS}, the GRanulation And Spectrum Simulator. \revise{We envision that \grass\ may be useful for training and validating various strategies for reducing the effects of stellar variability on precision Doppler measurements. In particular, mitigation strategies that make use of line-shape information could be tested on data sets generated by \grass. } \par

In the following sections, we describe \grass\ in detail. In \S\ref{data}, we summarize the input observations used to create our model spectra, and briefly comment on the output of the simulation tool. In \S\ref{methods}, we discuss the processes by which \grass\ creates synthetic spectra from the input solar observations. In \S\ref{validation}, we validate the \grass\ modeling approach by comparison to disk-integrated reference observations. In \S\ref{results}, we present some first results obtained from \grass\ single-line simulations. In \S\ref{discussion}, we comment on some potential uses, discuss future avenues, and also highlight the limitations and caveats of \grass. \par

%% === data === 
\section{Data} \label{data}

Rather than using MHD and radiative transfer simulations to produce synthetic spectra \citep[as in previous studies; e.g.,][]{Cegla2018, Cegla2019a}, we instead use disk-resolved, high-resolution observations of the Sun to create our synthetic disk-integrated spectra. This modeling approach offers a number advantages. Principally, we know that our model captures the most important physics precisely because it is based on real data. Although the current version of \grass\ explicitly excludes phenomena such as spots, this is in principle a solvable problem with additional observations or modeling. Our input observations are described below, in \S \ref{subsec:input_data}. In \S \ref{subsec:output_data}, we briefly describe the output of \texttt{GRASS}, reserving a more comprehensive description of our methodology for \S \ref{methods}. \par

\subsection{Input Data Description} \label{subsec:input_data}
Since line-shape variations driven by granulation vary with time and location on the disk, synthesizing our model disk-integrated spectra requires temporally and spatially resolved input data. To account for these variations in line shape, we use a set of solar observations originally published in \citealt{Lohner-Bottcher2019} (hereafter \citetalias{Lohner-Bottcher2019}) as a template for line synthesis. We refer to these data as the ``input data." These input data consist of reduced spectra covering the Fe \textsc{I} 5434.5 \AA\ line, from which we measure bisectors and widths as a function of depth. Ideally, these data would be derived from high-resolution observations conducted simultaneously across the solar disk. To our knowledge, however, no such data set exists and obtaining such data would require a special-purpose instrument. Relevant spectroscopic parameters and quantities for the Fe \textsc{I} 5434.5 \AA\ line are summarized in Table~\ref{tab:feI}. \par

\subsubsection{Summary of Input Data Observations}

\input{tables/spectroscopic.tex}

The observations of this Fe line were carried out as described in \citealt{Lohner-Bottcher2018} (hereafter \citetalias{Lohner-Bottcher2018}). The observations\revise{, consisting of 20-minute sequences,} were performed using the Laser Absolute Reference Spectrograph \citep[LARS,][]{Doerr2015, Lohner-Bottcher2017} at the German Vacuum Tower Telescope (VTT). LARS employs VTT's high-resolution echelle spectrograph in combination with a laser frequency comb (LFC) to achieve superb spectral resolution $R \sim \lambda/\Delta\lambda \sim 7 \times10^{5}$ with an absolute wavelength calibration accuracy of $\sim$$0.02$ m\AA\ (about $1\ \ms$) in the wavelength region of interest. \par

To sample line bisectors along different lines of sight, observations were carried out at eleven positions along each of four directions from disk center, oriented along and perpendicular to the sky-projected solar rotation axis (see Figure~\ref{fig:one}). The positions are radially parameterized as $\mu = \cos(\theta)$, where the heliocentric angle $\theta$ is the angle subtended by the line of sight and the solar surface vertical. The parameter $\mu$ is therefore 1 at disk-center and 0 at the limb edge. Individual observations \revise{had a $\sim$10\arcsec\ field of view set by the fiber-coupling unit and} were performed with a pointing accuracy of $\sim$1\arcsec. \par

To average over supergranular motions which would hinder the precise convective blueshift measurements performed in \citetalias{Lohner-Bottcher2018} and \citetalias{Lohner-Bottcher2019}, observations at each limb position were quickly scanned over ellipses with area corresponding to the typical angular area of supergranules. \revise{The sizes and orientations of the ellipses were varied with position on the disk in order to account for the effects of foreshortening. At disk center, a circular scan pattern was used, with a total diameter of $\sim$30\arcsec\ accounting for the size of the fiber-coupling unit. Slightly away from disk center (from around $\mu = 0.95$ to $0.7$), where the amplitudes of $p$-modes dominate over motions from supergranulation, the scanning ellipses had total axes dimensions of about 40\arcsec$\times$10\arcsec\ (i.e., including the width of the fiber-coupling unit). Toward the limb ($\mu \leq 0.5$), where horizontal supergranular motions dominate over $p$-modes, the total ellipse axes dimensions were about 40\arcsec$\times$30\arcsec.} \par

Observations were carried out in \revise{sequences of} $\sim$20 minutes in length, with individual exposures conducted at a cadence of 1.5 seconds and then binned into ten-exposure (15-second) bins. To avoid \revise{the systematic effect of changes in convective blueshift} introduced by active regions, simultaneous $G$-band images from the LARS context camera and recent magnetograms from the Solar Dynamics Observatory (SDO) Helioseismic Magnetic Imager \citep[HMI,][]{Pesnell2012, Scherrer2012} were used to ensure that only quiet Sun regions were observed. \revise{In the case of the HMI magnetograms, the automatically identified active region patches, which are flagged by the data reduction pipeline as pixels with an absolute line-of-sight magnetic field strength greater than 100 G, were used to reject active regions \citep{Hoeksema2014}.} Subsequent data reduction, including absolute wavelength calibration and corrections for barycentric motion and solar rotation, were performed as described in \citet{Lohner-Bottcher2017} and \citetalias{Lohner-Bottcher2018}. For lines observed by \citetalias{Lohner-Bottcher2018} and \citetalias{Lohner-Bottcher2019}, the \revise{observed} wavelengths of solar lines were empirically measured \revise{with respect to the lab-frame wavelengths of Fe \textsc{I} lines to an accuracy of below $0.1$ m\AA, or about $2-4\ \ms$,} using the \revise{LARS LFC in combination with a} hollow cathode lamp. \par

\subsection{Output Data} \label{subsec:output_data}
As we describe in detail in \S \ref{methods}, we spatially interpolate and integrate the input data to create synthetic time series spectra like those for an unresolved point source. We refer to these spectra, and the associated cross-correlation functions and velocities, as the ``output data" of the simulation. \par

%% === methods === 
\section{Software Description and Methods} \label{methods}

\subsection{Program Language, Installation, and Performance}
The latest version of \grass\ and its associated documentation are available from GitHub\footnote{\url{https://github.com/palumbom/GRASS}}. \revise{The frozen version of \grass\ accompanying this work (v1.0) is archived on Zenodo \citep{GRASS}.} \grass\ is written entirely in \texttt{Julia}\footnote{\url{https://julialang.org}}, a high-level, performance-oriented language. To generate synthetic spectra, the user must specify some input parameters in a brief \texttt{Julia} script (see the associated documentation and tutorials on GitHub). In addition to the output spectra, users can choose to store derived data products such as cross-correlation function (CCF) profiles and/or apparent radial velocities measured from the spectra using one of several algorithms. \par

\grass\ was designed to produce synthetic disk-integrated spectra more quickly than can be done through MHD and radiative transfer simulations. The compute-time and memory requirements of \grass\ are primarily dictated by three parameters: the grid size of the simulated disk ($N^2$, see \S\ref{subsec:res}), the number of time-steps simulated ($N_t$, with one step corresponding to one 15-second input observation), and the number of spectral resolution elements synthesized ($N_\lambda$). We find that the computation time scales quadratically with $N$, and linearly with both $N_t$ and $N_\lambda$. For this work, we simulate single-line spectra to validate \grass\ against reference disk-integrated observations. For these runs of \grass, we use \revise{$N^2 = 132^2$}, $N_t = 50$, and $N_\lambda = 193$ (corresponding to a spectrum 1.5 \AA\ wide with spectral resolution $R = 7\times10^5$ at $\lambda = 5434.5$ \AA). Depending on the exact hardware configuration, we find that we can generate 50 instances of output spectra in less than \revise{thirty seconds} on desktop hardware. \par

\subsection{Creating Synthetic Spectra} \label{subsec:create}
\grass\ is designed to create realistic time series of synthetic spectra with granulation-driven line-shape variation. The creation of these synthetic spectra from the input data is carried out in three broad steps, which we describe in the subsequent sections:

\begin{itemize}
    \item initial``pre-processing" of the input data, in which the reduced spectra are used to \revise{measure line bisectors and widths} as functions of depth within the line (\S \ref{subsubsec:preprocess}),
    \item simulation of a spatially-resolved stellar disk, in which the pre-processed data are used to re-create synthetic disk-resolved line profiles on a model stellar disk (\S\ref{sec:resolved_disk}),
    \item and spatial integration of the model stellar disk, in which the simulated disk-resolved spectra are co-added into a disk-integrated spectrum like those observed for point sources (\S\ref{sec:disk_int}).
\end{itemize}

The output data consisting of disk-integrated, time-series synthetic spectra can optionally be binned and used to compute cross-correlation functions and apparent radial velocities, as is typical for current RV surveys. We detail our procedure for these computations in \S\ref{subsubsec:obs} and \S\ref{subsec:veloc}. \par

\subsubsection{Input Data Pre-processing}
\label{subsubsec:preprocess}

\input{captions/fig2.tex}

As described in \S\ref{subsec:input_data}, the input solar data are reduced spectra binned to a 15-second cadence. To uniquely specify line shape from the core to the wings, we directly measure line bisectors and widths as functions of depth from these reduced spectra. To do so, we isolate the section of the reduced spectrum containing only the observed line of interest (i.e., the Fe \textsc{I} 5434.5 \AA\ line), which we then interpolate onto an evenly-sampled intensity grid. The width at each depth is then calculated as the difference in wavelength between the red and blue sides of the line, and the bisector as the average. \par

In implementation, we perform a number of additional steps to produce smooth and accurate bisector and width measurements. We first average the flux across adjacent pixels in areas where the line profile is not smooth. To circumvent the impact of shallow line blends in the line wings, we model the far line wings above 93\% continuum level as Voigt functions. We use separate non-linear least squares fits of the red-ward and blue-ward wings (excluding pixels containing significant blends) to determine the best model parameters. Since the uncertainty in the bisector measurement increases where the slope in the line is small \citep{Gray2008}, we find that the top-most bisector measurements are quite inaccurate. To avoid the impact of these spurious measurements, we model the bisectors above 80\% continuum flux as the linear extrapolation of the bisector data measured between 70\% and 80\% continuum flux. \par

For many limb positions, the full sequence of input data were not observed continuously. Often, several minutes of spectra were observed in one session, with the other session observed months later. In these cases, we adjust the mean velocity of the latter bisector series to match that of the first. For all results presented in this paper, we have performed additional simulations using only the longest set of contiguous data for each limb position. We find no significant difference in our results between these two sets of simulations. However, caution should nevertheless be taken when producing or interpreting series of spectra longer than $\sim$20 minutes. \par

In some cases, we exclude highly spurious instances of the input data. We discard any epochs for which the bisector is more than $3\sigma$ removed from the mean bisector measurement at a given intensity and limb position. Due to apparent errors in the raw spectra reduction, we also entirely discard the data collected on 2017/10/17 for $\mu = 0.7$ on the northern solar axis. We instead only use the data for this position collected in 2016. Although this reduces the total time-baseline of available data, this section of the Sun only contributes $\sim$$4\%$ to the total disk-integrated flux in our simulations. \par

Example pre-processed bisectors and width measurements are shown in Figure~\ref{fig:two}. Variability from pulsations and granulation are clearly visible in the bisectors. Whereas pulsations largely only change the horizontal position (i.e., velocity) of the bisector curves, granulation can change the curvature, shape, and position of individual bisectors. The line width measurements do exhibit a small degree of variability, though the level of variability is very small compared to that of the bisectors. \par

The initial pre-processing described above is performed only once, and the resulting bisectors and width measurements are written to output files that are included in the \grass\ GitHub repository. Upon execution of \grass, the files containing these pre-processed data are read into memory and sorted into arrays that are assigned $\mu$ and axis \revise{(i.e., North, East, South, West with respect to the solar rotation axis)} identifiers. For each unique \revise{$(\mu{\rm,\ axis})$} pair, the corresponding array contains the full time-series of pre-processed bisectors and width measurements for that disk position. As detailed in the subsequent sections, these data are then used to generate synthetic absorption line profiles. \par

\subsubsection{Adjusting Input Line Depths} \label{sec:scale_chop}

Following from the detailed explanation of stellar line formation presented in \citet{Gray2008}, we \revise{can} use the information encoded in the deep Fe \textsc{I} 5434.5 \AA\ line to also model shallower lines. As explained in Chapter 17 of \citet{Gray2008} and shown in their Figure 17.14, the bisectors of shallower lines resemble the upper portions of the bisectors of deeper lines. This fact is driven by the nature of deep line formation in stellar atmospheres. Because the intensity in a given portion of a line is controlled by the source function at a corresponding physical depth in the stellar atmosphere, the wings of deep lines, which form deep in the photosphere, may be thought of as shallow lines themselves. Lines from species with identical lower energy-level abundance distributions should therefore share line profiles. Given this fact, we have written \grass\ to allow the user to generate synthetic lines of arbitrary continuum-normalized depths, assuming that the information encoded in the deep Fe \textsc{I} 5434.5 \AA\ line samples velocity structure along deep slant depths in the solar atmosphere. \par

To model shallower lines, \grass\ must transform the pre-processed input data. In the case of the width measurements, \grass\ simply scales the data onto the new range of intensities for the shallower line. For the bisector measurements, \grass\ discards measurements for intensities below the depth of the line and interpolates the remaining points onto a same-length grid. \revise{Since the input line bisectors are extrapolated above 80\% of the continuum level, synthetic lines of depths less than 20\% are based solely on extrapolated data.} The consequences of this approach with respect to Doppler velocity measurements are analyze and discussed in \S\ref{sec:depth_var}. \par

\subsubsection{Simulating a Stellar Disk} \label{sec:resolved_disk}
Following the initial pre-processing of the input data, \grass\ models a stellar disk by creating a uniform Cartesian $xy$ spatial grid of $N \times N$ pixels. The model stellar disk is described by a unit circle inscribed within the square grid. At each point on this model disk, \grass\ creates a synthetic, spatially-resolved spectrum consisting of any number of synthetic lines specified by the user. To create the synthetic line profiles, \grass\ first finds the nearest solar axis and value of $\mu$ to the point of interest on the grid. Then, it identifies the corresponding input solar observations and chooses a starting epoch from the input data. This epoch is chosen randomly for each spatial grid cell, which ensures that synthetic lines in separate spatial cells do not move in concert. \par

On a given spatial grid cell, \grass\ synthesizes each absorption line by using the input data to assign the wavelength at each depth for the left- and right-hand sides of the synthetic line. The resulting absorption line profile, which is initially specified on a uniform grid of intensities, is then interpolated onto a uniform wavelength grid of the spectral resolution specified by the user. This process is repeated for any additional synthetic lines. When lines are sufficiently close (i.e., in the case of blends), the separate absorption profiles are multiplied to create a blended line profile.  \par

After all lines have been synthesized within a given spatial cell, \grass\ applies a rotational Doppler shift based on the position of the cell on the disk. We use the differential rotation model from \citet{Snodgrass1990}, where the angular rotational velocity $\omega$ varies as a function of a solar latitude $\phi$:

\begin{align}
    \omega(\phi) &= A + B \sin^2\phi + C \sin^4 \phi \\
    A &= 14.713 ^{\circ}/{\rm day} \\
    B &= -2.396 ^{\circ}/{\rm day} \\
    C &= -1.787 ^{\circ}/{\rm day}
\end{align}

\noindent We use the best-fit values reported in \citet{Snodgrass1990} for the coefficients $A$, $B$, and $C$. The true rotational velocity $v_{\rm rot}$ at some latitude $\phi$ is then calculated as:

\begin{align}
    v_{\rm rot} &= v_0 / \omega(\phi) \\
    v_0 &= 0.000168710673\ {\rm R_*/day/}c
\end{align}

\noindent where $c$ is the speed of light, and the stellar radius $R_*$ is set to unity. This velocity is then projected onto the line of sight for the given sky-projected inclination of the rotation axis. The default inclination is given by the 3D unit vector $(0,1,0)$ corresponding to an equator-on star. We note that this calculation, as well as the spatial $xy$ grid, assume a spherical star (observed as a circle in projection). In the case of rapidly rotating stars, this assumption may not be valid. \par

In addition to the effects of differential rotation, \grass\ must also account for limb darkening. To obtain $I_\mu$, the limb-darkened intensity at a given $\mu$, we use a simple wavelength-independent, quadratic limb darkening law from \citet{Kopal1950}:

\begin{equation}
\frac{I_\mu}{I_0} = 1 - u_1 (1-\mu) - u_2 (1-\mu)^2, 
\end{equation}

\noindent where the default values for the coefficients are $u_1 = 0.4$ and $u_2 = 0.26$, typical solar values for this wavelength region \citep[as verified via][]{Southworth2015}. We take $I_0$, the intensity at disk center, to be 1. For simulations of other wavelength regions or stars with different limb darkening behavior, the limb darkening coefficients may be easily changed by the user. \par

\subsubsection{Integrating Over the Stellar Disk} \label{sec:disk_int}
As described in the previous sections, \grass\ essentially constructs the intensity as a function of time $t$, wavelength $\lambda$, and position on the disk $(x, y)$: $I(t, \lambda, x, y$).  To create a spatially-integrated spectrum for a point source $I(t, \lambda)$, we sum intensities over the spatial dimensions:

\begin{equation}
    I(t, \lambda) = C \sum_{i=1}^N\sum_{j=1}^N  I(t, \lambda, x_{i}, y_{j})
\end{equation}
